Internal models of type theory and internal higher categories for the Univalent Foundations

### 2014-02-28 article-models-tt.tex
fixing a removed label

\begin{proof}
To prove the first judgmental equality, note that
\begin{align*}
w & \jdeq \subst{w}{\idfunc[\ctxext{A}{P}]} \tag{by \autoref{idfunc-subst-defn}}\\
& \jdeq \subst{w}{\subst{\idfunc[P]}{{\ctxwk{P}{\idfunc[A]}}{\idfunc[\ctxwk{\ctxext{A}{P}}{\ctxext{A}{P}}]}}}
  \tag{by \autoref{idfunc-ext-comp}}\\
& \jdeq \subst{{w}{\idfunc[P]}}{\subst{w}{{\ctxwk{P}{\idfunc[A]}}{\idfunc[\ctxwk{\ctxext{A}{P}}{\ctxext{A}{P}}]}}}\tag{by \autoref{comp-ss-4}}\\
& \jdeq \subst{{w}{\idfunc[P]}}{{\subst{w}{\ctxwk{P}{\idfunc[A]}}}{\subst{w}{\idfunc[\ctxwk{\ctxext{A}{P}}{\ctxext{A}{P}}]}}}\tag{by \autoref{comp-ss-2}}\\
& \jdeq \subst{{w}{\idfunc[P]}}{{\subst{w}{\ctxwk{P}{\idfunc[A]}}}{\subst{w}{\ctxwk{\ctxext{A}{P}}{\idfunc[\ctxext{A}{P}]}}}}\tag{by \autoref{idfunc-wk-comp}}\\
& \jdeq \subst{{w}{\idfunc[P]}}{{\subst{w}{\ctxwk{P}{\idfunc[A]}}}{\idfunc[\ctxext{A}{P}]}}\tag{by \autoref{defn-ws-2}}\\
& \jdeq \ctxext{\cprojfst{A}{P}{w}}{\cprojsnd{A}{P}{w}}\tag{by definition}
\end{align*}
\end{proof}

>>>>

\begin{proof}
To prove the first judgmental equality, note that
\begin{align*}
w & \jdeq \subst{w}{\idfunc[\ctxext{A}{P}]} \tag{by \autoref{idfunc-subst-defn}}\\
& \jdeq \subst{w}{\subst{\idfunc[P]}{{\ctxwk{P}{\idfunc[A]}}{\idfunc[\ctxwk{\ctxext{A}{P}}{\ctxext{A}{P}}]}}}
  \tag{by \autoref{idfunc-ext-comp}}\\
& \jdeq \subst{{w}{\idfunc[P]}}{\subst{w}{{\ctxwk{P}{\idfunc[A]}}{\idfunc[\ctxwk{\ctxext{A}{P}}{\ctxext{A}{P}}]}}}\tag{by \autoref{comp-ss-4}}\\
& \jdeq \subst{{w}{\idfunc[P]}}{{\subst{w}{\ctxwk{P}{\idfunc[A]}}}{\subst{w}{\idfunc[\ctxwk{\ctxext{A}{P}}{\ctxext{A}{P}}]}}}\tag{by \autoref{comp-ss-4}}\\
& \jdeq \subst{{w}{\idfunc[P]}}{{\subst{w}{\ctxwk{P}{\idfunc[A]}}}{\subst{w}{\ctxwk{\ctxext{A}{P}}{\idfunc[\ctxext{A}{P}]}}}}\tag{by \autoref{idfunc-wk-comp}}\\
& \jdeq \subst{{w}{\idfunc[P]}}{{\subst{w}{\ctxwk{P}{\idfunc[A]}}}{\idfunc[\ctxext{A}{P}]}}\tag{by \autoref{defn-ws-2}}\\
& \jdeq \ctxext{\cprojfst{A}{P}{w}}{\cprojsnd{A}{P}{w}}\tag{by definition}
\end{align*}
\end{proof}
